Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-04 analysis/paper/Rmd/methods.Rmd
fixed figure refs

@keller2018genetic identified five expression trait hotspots in their
study of pancreatic islet gene expression in 378 Diversity Outbred mice. They
defined a hotspot to be a 4-Mb region that affects at least 100 nonlocal expression
traits.

@@

In all of our mediation analyses, the nonlocal transcripts are the targets, while the local
transcripts serve as candidate mediators of the QTL-target relationship. 
We only considered as potential mediators those local traits with strong univariate LODs.
In Equations~\ref{model1} through \ref{model4}, $X$ is a matrix of founder allele dosages,
$B$ is a matrix
of founder allele effects, $W$ is a matrix of covariates, $C$ is a matrix of covariate
effects, $M$ is a vector of values for a single candidate mediator (a local expression trait, in our case), $\beta$ is the effect
of the mediator on the complex trait (after adjusting for other covariates in the model), 1 is a vector with all entries set to 1, $\alpha$
is a parameter that corresponds to the mean trait value (after adjusting for other covariates in the model), and $E$ is a vector of normally distributed random errors.

>>>>

@keller2018genetic performed univariate QTL mapping for all expression traits. 
They identified five expression trait hotspots in their
study of pancreatic islet gene expression in 378 Diversity Outbred mice. They
defined a hotspot to be a 4-Mb region that affects at least 100 nonlocal expression
traits.

@@

In all of our mediation analyses, the nonlocal transcripts are the targets, while the local
transcripts serve as candidate mediators of the QTL-target relationship. 
We only considered as potential mediators those local traits with strong univariate LODs.
In Equations~\ref{eq:model1} through \ref{eq:model4}, $X$ is a matrix of founder allele dosages,
$B$ is a matrix
of founder allele effects, $W$ is a matrix of covariates, $C$ is a matrix of covariate
effects, $M$ is a vector of values for a single candidate mediator (a local expression trait, in our case), $\beta$ is the effect
of the mediator on the complex trait (after adjusting for other covariates in the model), 1 is a vector with all entries set to 1, $\alpha$
is a parameter that corresponds to the mean trait value (after adjusting for other covariates in the model), and $E$ is a vector of normally distributed random errors.
